%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Peraton}{Jan 2025 -- Present}
    {Software Engineering Intern}{Herndon, VA}
    \resumeItemListStart
        \resumeItem{Built Python based LLM agents with Retrieval Augmented Generation (RAG), tool calling, and iterative workflows in a modular agentic framework.}
        \resumeItem{Engineered a persistent memory system using PostgreSQL to enable agents to recall user-specific data and tailor responses with long term context.}
        \resumeItem{Developed analytics infrastructure to track token usage, cost, and user behavior across the LLM platform, supporting customer budgeting and system monitoring. Built a dashboard to display this data via FastAPI and React.}
        \resumeItem{Created a corresponding analytics agent that converts user prompts into SQL queries, outputs to CSV, and invokes Jupyter notebooks in Docker containers to auto-generate interactive data visualizations.}
        \resumeItem{Implemented a citation system that associates outputs with original RAG and SQL sources to reduce hallucinations.}
        \resumeItem{Contributed to Gradio based LLM interfaces, and maintained CI-ready Docker environments.}
        \resumeItem{Collaborated in Agile sprints using Jira, Git, and rigorous code review practices in a fast paced environment.}
    \resumeItemListEnd
    
    \resumeSubheading
    {BrightVine Solutions}{May 2023 -- Aug 2023, May 2024 -- Aug 2024}
    {Software Engineering Intern}{Remote}
    \resumeItemListStart
        \resumeItem{Built an Azure OpenAI integrated chatbot that converts natural language to SQL with client specific fine-tuning, saving time for business users.}
        \resumeItem{Designed and deployed a batch import error handling system using SQL, C\#, and XML to production.}
        \resumeItem{Closed full stack tickets across frontend and backend systems, contributing to product enhancements and bug fixes.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Virginia Tech Department of Computer Science}{Jan 2023 -- December 2024}
    {Teaching Assistant, CS 1064: Intro to Python}{Blacksburg, VA}
    \resumeItemListStart
        \resumeItem{Supported 2000+ students by mentoring, debugging, and answering questions on foundational Python coding.}
        \resumeItem{Graded and provided feedback on hundreds of coding projects, assessments, and essays to reinforce best practices.}
    \resumeItemListEnd

\resumeSubHeadingListEnd